A seamless, client-centric programming model for type safe web applications

### 2014-05-02 paper.tex
Add GWT to related work.

@@

>>>>

\paragraph{Google Web Toolkit} Google Web Toolkit\ \cite{gwt}, a Java
compiler targeting the browser, provides its own solution to client-server
interoperability as well. This solution is based on callbacks, forcing
developers to code in a confusing continuation passing style. It also suffers
from excessive boilerplate code and an error-prone configuration process.

@@

\bibitem[Wargolet (2011)]{gwt}
S. Wargolet. "Google Web Toolkit. Technical report 12." University of Wisconsin-Platterville Department of Computer Science and Software Engineering, 2011.
